|

### 2022-12-23 paper.Rmd
autogit

![Airfoil - Average Population Diversity](./img/airfoil_FullRun_30gens/mean_popDiversity_byGens.png)
Since @dae-gp_2022_symreg finds, that DAE-GP finds higher quality and smaller sized solutions smaller than average GP for a given number of 10.000 the airfoil problem

>>>>

![Airfoil - Average Population Diversity](./img/airfoil_FullRun_30gens/mean_popDiversity_byGens.png)
Since @dae-gp_2022_symreg shows, that DAE-GP finds higher quality that are also smaller in size than those found by average GP for a given number of 10.000 fitness evaluations, I also studied the differences in average solution size between pre-trained and regular DAE-GP.

### 2022-12-23 paper.tex
autogit

\usepackage[numbers]{natbib}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}

@@

After closely examining the effect of pre-training on DAE-GPs
generalization behaviour another series of experiments is conducted to
study how pre-training influences the overall search behaviour of
DAE-GP. Again the Airfoil problem was selected as a first benchmark
problem to test pre-trained DAE-GP against traditional DAE-GP
{[}\textbf{gp\_2022\_symreg?}{]}, the parameters are described in table
\(A\)

@@

Regarding the hidden neurons, the dimension of each hidden layer, I used
two different strategies: Regular DAE-GP uses the same strategy as
described by earlier work (see {[}\textbf{gp\_2022\_symreg?}{]} or
{[}18{]}), the number of hidden neurons is dynamically set at each
generation to the maximum length of all solutions inside the current
training population. For pre-trained DAE-GP another strategy had to be
used, we use a fixed number of hidden neurons for each run that is set
equal to the maximum length of all individuals that are present in the
initial pre-training population.

>>>>

@@

After closely examining the effect of pre-training on DAE-GPs
generalization behaviour another series of experiments is conducted to
study how pre-training influences the overall search behaviour of
DAE-GP. Again the Airfoil problem was selected as a first benchmark
problem to test pre-trained DAE-GP against traditional DAE-GP {[}17{]},
the parameters are described in table \(A\)

@@

Regarding the hidden neurons, the dimension of each hidden layer, I used
two different strategies: Regular DAE-GP uses the same strategy as
described by earlier work (see {[}17{]} or {[}18{]}), the number of
hidden neurons is dynamically set at each generation to the maximum
length of all solutions inside the current training population. For
pre-trained DAE-GP another strategy had to be used, we use a fixed
number of hidden neurons for each run that is set equal to the maximum
length of all individuals that are present in the initial pre-training
population. I decided to take this aproach instead of using a fixed
number of hidden neurons for the fact that it simplifies the adjustment
of the parameter for later experiments on different problems. It should
nonetheless be mentioned that this strategy does give pre-training on
average more hidden neurons per layer resulting in a more complex
network (since the pre-training population is much larger than the
regular population, the chances for larger individuals inside it are
also higher).

\begin{figure}
\centering
\includegraphics{./img/airfoil_FullRun_30gens/mean_median_fitness_byGens.png}
\caption{Airfoil - Best Fitness over 30 Generations}
\end{figure}

\begin{figure}
\centering
\includegraphics{./img/airfoil_FullRun_30gens/final_fit_boxplot.png}
\caption{Airfoil - Fitness Distribution Boxplot}
\end{figure}

\includegraphics{./img/airfoil_FullRun_30gens/mean_popDiversity_byGens.png}
Since {[}17{]} shows, that DAE-GP finds higher quality that are also
smaller in size than those found by average GP for a given number of
10.000 fitness evaluations, I also studied the differences in average
solution size between pre-trained and regular DAE-GP.

\begin{figure}
\centering
\includegraphics{./img/airfoil_FullRun_30gens/mean_Size_byGens.png}
\caption{Airfoil - Average Solution Size}
\end{figure}
